---
title: "Running MCMCglmm with mulTree and 100 Random Trees"
author: "Nations"
date: "11/01/2018"
output:
  html_document: default
  pdf_document: default
---

Bayesian logistic mixed models for philippine murine climbing data

#### Warning
This takes a long time to run, and creates many files in the directory.
See mulTree documentation for more information

Set root directory
```{r}
knitr::opts_knit$set(root.dir = "~/Documents/.......")
```


```{r}
library(ape)
library(geiger)
library(phytools)
library(ggplot2)
library(plyr)
library(dplyr)
library(MCMCglmm)
library(tidyr)
library(coda)
library(parallel)
library(ggridges)
library(mulTree)
library(cowplot)
```



```{r}
getwd()
```

reading in a sample of 4000 trees, and subsampling.
```{r}
trees <- read.nexus("4000.trees")
tree_samp <- sample(trees, size = 100)
#test_samp <- sample(trees, size = 2)
tree <- read.newick("Tree.nwk")
```



mul_data 
```{r}
mul_data <- read.csv("Phil_MulTree.csv", header=T)
# reorder data by tree labels
mul_data <- mul_data[order(factor(mul_data$Species, levels = tree$tip.label)), ]
```


#### Universal Parameters
```{r}
mulTree_data <- as.mulTree(data = mul_data, tree = tree_samp, taxa = "Species", rand.terms = ~ Species + phylo)

## The MCMC parameters (generations, sampling, burnin)
my_parameters <- c(1000000, 2000, 100000)
#my_parameters <- c(10000, 100, 5000)
```

MANUS
```{r}
manus_formula <-climb ~ MANUS

prior_MANUS <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~MANUS, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = manus_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.MANUS_tree",
        priors = prior_MANUS,
        parallel = "SOCK"
        )
```

```{r}
z.MANUS <- read.mulTree("z.MANUS_tree")
str(z.MANUS)
MANUS_results <- summary(z.MANUS, use.hdr = T, cent.tend = mean, prob = c(95, 5))
MANUS_results
```

SMI
```{r}
smi_formula <-climb ~ SMI

prior_SMI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~SMI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = smi_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.SMI_tree",
        priors = prior_SMI,
        parallel = "SOCK"
        )
```

```{r}
z.SMI <- read.mulTree("z.SMI_tree")
str(z.SMI)
SMI_results <- summary(z.SMI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
SMI_results
```

BI
```{r}
bi_formula <-climb ~ BI

prior_BI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~BI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = bi_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.BI_tree",
        priors = prior_BI,
        parallel = "SOCK"
        )
```

```{r}
z.BI <- read.mulTree("z.BI_tree")
str(z.BI)
BI_results <- summary(z.BI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
BI_results
```

HRI
```{r}
hri_formula <-climb ~ HRI

prior_HRI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~HRI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = hri_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.HRI_tree",
        priors = prior_HRI,
        parallel = "SOCK"
        )
```

```{r}
z.HRI <- read.mulTree("z.HRI_tree")
str(z.HRI)
HRI_results <- summary(z.HRI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
HRI_results
```

HEB
```{r}
heb_formula <-climb ~ HEB

prior_HEB <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~HEB, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = heb_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.HEB_tree",
        priors = prior_HEB,
        parallel = "SOCK"
        )
```

```{r}
z.HEB <- read.mulTree("z.HEB_tree")
str(z.HEB)
HEB_results <- summary(z.HEB, use.hdr = T, cent.tend = mean, prob = c(95, 5))
HEB_results
```

OLI
```{r}
oli_formula <-climb ~ OLI

prior_OLI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~OLI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = oli_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.OLI_tree",
        priors = prior_OLI,
        parallel = "SOCK"
        )
```

```{r}
z.OLI <- read.mulTree("z.OLI_tree")
str(z.OLI)
OLI_results <- summary(z.OLI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
OLI_results
```

URI
```{r}
uri_formula <-climb ~ URI

prior_URI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~URI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = uri_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.URI_tree",
        priors = prior_URI,
        parallel = "SOCK"
        )
```

```{r}
z.URI <- read.mulTree("z.URI_tree")
str(z.URI)
URI_results <- summary(z.URI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
URI_results
```

CI
```{r}
ci_formula <-climb ~ CI

prior_CI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~CI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = ci_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.CI_tree",
        priors = prior_CI,
        parallel = "SOCK"
        )
```

```{r}
z.CI <- read.mulTree("z.CI_tree")
str(z.CI)
CI_results <- summary(z.CI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
CI_results
```

FRI
```{r}
fri_formula <-climb ~ FRI

prior_FRI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~FRI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = fri_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.FRI_tree",
        priors = prior_FRI,
        parallel = "SOCK"
        )
```

```{r}
z.FRI <- read.mulTree("z.FRI_tree")
str(z.FRI)
FRI_results <- summary(z.FRI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
FRI_results
```

GI
```{r}
gi_formula <-climb ~ GI

prior_GI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~GI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = gi_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.GI_tree",
        priors = prior_GI,
        parallel = "SOCK"
        )
```

```{r}
z.GI <- read.mulTree("z.GI_tree")
str(z.GI)
GI_results <- summary(z.GI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
GI_results
```

FEB
```{r}
feb_formula <-climb ~ FEB

prior_FEB <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~FEB, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = feb_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.FEB_tree",
        priors = prior_FEB,
        parallel = "SOCK"
        )
```

```{r}
z.FEB <- read.mulTree("z.FEB_tree")
str(z.FEB)
FEB_results <- summary(z.FEB, use.hdr = T, cent.tend = mean, prob = c(95, 5))
FEB_results
```

TRI
```{r}
tri_formula <-climb ~ TRI

prior_TRI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~TRI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = tri_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.TRI_tree",
        priors = prior_TRI,
        parallel = "SOCK"
        )
```

```{r}
z.TRI <- read.mulTree("z.TRI_tree")
str(z.TRI)
TRI_results <- summary(z.TRI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
TRI_results
```

TSI
```{r}
tsi_formula <-climb ~ TSI

prior_TSI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~TSI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = tsi_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.TSI_tree",
        priors = prior_TSI,
        parallel = "SOCK"
        )
```

```{r}
z.TSI <- read.mulTree("z.TSI_tree")
str(z.TSI)
TSI_results <- summary(z.TSI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
TSI_results
```

PES
```{r}
pes_formula <-climb ~ PES

prior_PES <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~PES, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = pes_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.PES_tree",
        priors = prior_PES,
        parallel = "SOCK"
        )
```

```{r}
z.PES <- read.mulTree("z.PES_tree")
str(z.PES)
PES_results <- summary(z.PES, use.hdr = T, cent.tend = mean, prob = c(95, 5))
PES_results
```

IM
```{r}
im_formula <-climb ~ IM

prior_IM <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~IM, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = im_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.IM_tree",
        priors = prior_IM,
        parallel = "SOCK"
        )
```

```{r}
z.IM <- read.mulTree("z.IM_tree")
str(z.IM)
IM_results <- summary(z.IM, use.hdr = T, cent.tend = mean, prob = c(95, 5))
IM_results
```

SI
```{r}
si_formula <-climb ~ SI

prior_SI <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~SI, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = si_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.SIS_tree",
        priors = prior_SI,
        parallel = "SOCK"
        )
```

```{r}
z.SI <- read.mulTree("z.SIS_tree")
str(z.SI)
SI_results <- summary(z.SI, use.hdr = T, cent.tend = mean, prob = c(95, 5))
SI_results
```

TAIL
```{r}
tail_formula <-climb ~ TAIL

prior_TAIL <- list(
    B = list(mu = rep(0, 2), 
             V=gelman.prior(~TAIL, data = mul_data, scale = sqrt(pi^2/3+1))), 
    G = list(G1 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1),   
             G2 = list(V = 1, nu = 100, alpha.mu = 0, alpha.V = 1)),
    R = list(V = 1, fix = 1) 
)

mulTree(mulTree.data = mulTree_data,
        formula = tail_formula,
        #random = ~ Species + phylo,
        rcov = ~ trait:units,
        family = "categorical",
        parameters = my_parameters,
        ESS = 20,
        chains = 2,
        verbose = FALSE,
        output = "z.TAIL_tree",
        priors = prior_TAIL,
        parallel = "SOCK"
        )
```

```{r}
z.TAIL <- read.mulTree("z.TAIL_tree")
str(z.TAIL)
TAIL_results <- summary(z.TAIL, use.hdr = T, cent.tend = mean, prob = c(95, 5))
TAIL_results
```



#### Get Beta Posteriors from all the models and Save
```{r}
post<- cbind(z.MANUS$MANUS, z.SMI$SMI, z.BI$BI, z.HRI$HRI, z.HEB$HEB, z.OLI$OLI, z.URI$URI, z.CI$CI, z.FRI$FRI, z.GI$GI, z.FEB$FEB, z.TRI$TRI, z.TSI$TSI, z.PES$PES, z.IM$IM, z.SI$SI, z.TAIL$TAIL)
colnames(post) <- c("MANUS","SMI","BI","HRI","HEB","OLI","URI","CI","FRI","GI","FEB","TRI","TSI","PES","IM","SI","TAIL")
rownames(post) <- 1:nrow(post)
post <- as.data.frame(post)
head(post)
write.csv(post, file = "20181101_posteriors.csv")
 post2 <- post %>%
  gather(frequency)
 write.csv(post2, file = "20181101_tidy_post.csv")
```


Read in posteriors and plot, removing "non significant" variables
```{r}
tpost <- read.csv("20181101_tidy_post.csv", header=T)
colnames(tpost)[colnames(tpost)=="frequency"] <- "m"
tpost$m = reorder(tpost$m, tpost$value, mean)

tpost2 <- tpost[ ! tpost$m %in% c("URI","TRI", "HRI", "GI", "FRI", "OLI", "FEB"), ]
```


Plotting figure 2
```{r}
 ggplot(tpost2, aes(x = value, y = m)) + 
  stat_density_ridges(quantile_lines = TRUE, quantiles = c(0.035, 0.975), rel_min_height = 0.02, scale = 2.1, calc_ecdf = T) +
  geom_vline(xintercept=0, linetype = "dotted" ) + 
  scale_y_discrete(expand = c(0.06, 0)) +
  scale_x_continuous(expand = c(0.01, 0)) +
  coord_cartesian(xlim=c(-70, 95)) +
  labs(x = expression("Posterior Probability of Regression Coefficient "*beta),y = "Index", center = TRUE) +
  theme_minimal(base_size = 11) + 
  theme(legend.position="none") 

output_file = "20181101_ALLTREE_index_grey_8.pdf"

ggsave(output_file, width = 7, height = 4)
```




