---
title: "Big_Run_BRMS"
output: html_document
---

Bayesian ordinal mixed models for categorical murine climbing data

#### Warning
This takes a long time to run

Set root directory
```{r}
knitr::opts_knit$set(root.dir = "~/Documents/....")
```


```{r}
library(ape)
library(geiger)
library(phytools)
library(ggplot2)
library(plyr)
library(dplyr)
library(MCMCglmm)
library(tidyr)
library(coda)
library(parallel)
library(ggridges)
library(mulTree)
library(brms)
library(cowplot)
```

```{r}
getwd()
```

reading in a sample of 4000 trees, and subsampling.
```{r}
trees <- read.nexus("4000.trees")
tree_samp <- sample(trees, size = 100)
#test_samp <- sample(trees, size = 2)
tree <- read.newick("Tree.nwk")
```

brms data
```{r}
data <- read.csv("ORDINAL_ALL.csv", header=TRUE)

data <- data[order(factor(data$Species, levels = tree$tip.label)), ]
```



# Now BRMS loops

Hypothesis for phylo signal
```{r}
hyp <- paste(
    "sd_phylo__Intercept^2 /", 
    "(sd_phylo__Intercept^2 + sd_Species__Intercept^2) = 0")
```

Trees for BRMS
```{r}
inverse<-list()
As <- list()

for (i in 1:length(tree_samp) ) {
  inverse[[i]] <- inverseA(tree_samp[[i]], nodes = "TIPS", scale = TRUE)
  x <- solve(inverse[[i]]$Ainv)
  rownames(x) <- rownames(inverse[[i]]$Ainv)
  As[[i]] <- x
}


#str(As)
```

####MANUS
```{r}
m.fit <- brm(
  State ~ MANUS + (1|phylo) + (1|Species), data = data, 
  family = cumulative(link = "probit"), cov_ranef = list(phylo = As[[1]]),
  iter = 5000,
  save_all_pars = TRUE,
  prior = c(
  set_prior("normal(0,50)", class = "b"),
  set_prior("normal(0,50)", class = "Intercept"),
  set_prior("normal(0,1.5)", class = "sd", coef = "Intercept", group = "Species"),
  set_prior("normal(0,1.5)", class = "sd", coef = "Intercept", group = "phylo")),
  control = list(adapt_delta = 0.99, max_treedepth = 15)
)
```


```{r}
m.fits <- vector("list", 100) 
for (i in seq_along(m.fits)) {
m.fits[[i]] <- update(m.fit,
                      cov_ranef = list(phylo = As[[i]],
                      cores = 4)
)
}
m.fits_comb <- combine_models(m.fits[[i]])
```

```{r}
summary(m.fits_comb)
plot(m.fits_comb)
plot(marginal_effects(m.fits_comb, "MANUS", categorical = TRUE))
pp_check(m.fits_comb)
(man_hyp <- hypothesis(m.fits_comb, hyp, class = NULL))
plot(man_hyp)
```


#### IM
```{r}
im.fit <- brm(
  State ~ IM + (1|phylo) + (1|Species), data = data, 
  family = cumulative(link = "probit"), cov_ranef = list(phylo = As[[1]]),
  iter = 5000,
  save_all_pars = TRUE,
  prior = c(
  set_prior("normal(0,50)", class = "b"),
  set_prior("normal(0,50)", class = "Intercept"),
  set_prior("normal(0,1.5)", class = "sd", coef = "Intercept", group = "Species"),
  set_prior("normal(0,1.5)", class = "sd", coef = "Intercept", group = "phylo")),
  control = list(adapt_delta = 0.99, max_treedepth = 15)
)
```

```{r}
im.fits <- vector("list", 100) 
for (i in seq_along(im.fits)) {
im.fits[[i]] <- update(im.fit,
                      cov_ranef = list(phylo = As[[i]],
                      cores = 4)
)
}
im.fits_comb <- combine_models(im.fits[[i]])
```

```{r}
summary(im.fits_comb)
plot(im.fits_comb)
plot(marginal_effects(im.fits_comb, "IM", categorical = TRUE))
pp_check(im.fits_comb)
(im_hyp <- hypothesis(im.fits_comb, hyp, class = NULL))
plot(im_hyp)
```

#### PES

```{r}
pes.fit <- brm(
  State ~ PES + (1|phylo) + (1|Species), data = data, 
  family = cumulative(link = "probit"), cov_ranef = list(phylo = As[[1]]),
  iter = 5000,
  save_all_pars = TRUE,
  prior = c(
  set_prior("normal(0,50)", class = "b"),
  set_prior("normal(0,50)", class = "Intercept"),
  set_prior("normal(0,1.5)", class = "sd", coef = "Intercept", group = "Species"),
  set_prior("normal(0,1.5)", class = "sd", coef = "Intercept", group = "phylo")),
  control = list(adapt_delta = 0.99, max_treedepth = 15)
)
```


```{r}
pes.fits <- vector("list", 100) 
for (i in seq_along(pes.fits)) {
pes.fits[[i]] <- update(pes.fit,
                      cov_ranef = list(phylo = As[[i]],
                      cores = 4)
)
}
pes.fits_comb <- combine_models(pes.fits[[i]])
```

```{r}
summary(pes.fits_comb)
plot(pes.fits_comb)
plot(marginal_effects(pes.fits_comb, "PES", categorical = TRUE))
pp_check(pes.fits_comb)
(pes_hyp <- hypothesis(pes.fits_comb, hyp, class = NULL))
plot(pes_hyp)
```


#### TAIL

```{r}
tail.fit <- brm(
  State ~ TAIL + (1|phylo) + (1|Species), data = data, 
  family = cumulative(link = "probit"), cov_ranef = list(phylo = As[[1]]),
  iter = 5000,
  save_all_pars = TRUE,
  prior = c(
  set_prior("normal(0,50)", class = "b"),
  set_prior("normal(0,50)", class = "Intercept"),
  set_prior("normal(0,1.5)", class = "sd", coef = "Intercept", group = "Species"),
  set_prior("normal(0,1.5)", class = "sd", coef = "Intercept", group = "phylo")),
  control = list(adapt_delta = 0.99, max_treedepth = 15)
)
```


```{r}
tail.fits <- vector("list", 100) 
for (i in seq_along(tail.fits)) {
tail.fits[[i]] <- update(tail.fit,
                      cov_ranef = list(phylo = As[[i]],
                      cores = 4)
)
}
tail.fits_comb <- combine_models(tail.fits[[i]])
```

```{r}
summary(tail.fits_comb)
plot(tail.fits_comb)
plot(marginal_effects(tail.fits_comb, "TAIL", categorical = TRUE))
pp_check(tail.fits_comb)
(tail_hyp <- hypothesis(tail.fits_comb, hyp, class = NULL))
plot(tail_hyp)
```


#### Density Overlay Plots (Sup figure, Posterior Checks)

```{r}
m_pp <- pp_check(m.fits_comb, nsamples = 100)
i_pp <- pp_check(im.fits_comb, nsamples = 100)
p_pp <- pp_check(pes.fits_comb, nsamples = 100)
t_pp <- pp_check(tail.fits_comb, nsamples = 100)
```

```{r}
m_p <- m_pp  + labs(title = "MANUS", center = TRUE) + theme(axis.text.x=element_blank())
```

```{r}
i_p <- i_pp  + labs(title = "IM", center = TRUE) + theme(axis.text.x=element_blank())
```

```{r}
p_p <- p_pp  + labs(title = "PES", center = TRUE) + theme(axis.text.x=element_blank())
```

```{r}
t_p <- t_pp  + labs(title = "TAIL", center = TRUE) + theme(axis.text.x=element_blank())
```

```{r}
ppc_plot <- plot_grid(m_p, i_p, p_p, t_p, ncol = 2, nrow = 2)
save_plot("20181101_PPcheck.pdf", ppc_plot, base_width = 7, base_height = 3.5)
```



#### Marginal Effects Plots! 

Manus
```{r}
m_eff <- marginal_effects(m.fits_comb, "MANUS", categorical = T, probs = c(0.1, 0.9))
```

```{r}
mem_plot <- plot(m_eff, plot = FALSE)[[1]] + 
scale_color_manual(labels = c("Terrestrial", "General", "Arboreal" ), 
                  values = c("1"="#d95f02", 
                                   "2"="#7570b3", 
                                   "3"="#1b9e77")) +
scale_fill_manual(labels = c("Terrestrial", "General", "Arboreal" ), 
                  values = c("1"="#d95f02", "2"="#7570b3", "3"="#1b9e77"),guide = F) + 
labs(x = "MANUS Index",
     center = F,
    color = "State") +
  theme_minimal() + 
  theme_ridges(center = T) +
  theme(axis.title.y = element_blank(), axis.title.x = element_text(size=7), axis.text.y  = element_text(size=4), axis.text.x = element_text(size=4),legend.position="none") 

mem_plot

output_file = "20181101_m_eff_MANUS.pdf"

ggsave(output_file, width = 9, height = 6)
```

IM
```{r}
i_eff <- marginal_effects(im.fits_comb, "IM", categorical = T, probs = c(0.1, 0.9))
```

Looks good!
```{r}
mei_plot <- plot(i_eff, plot = FALSE)[[1]] + 
scale_color_manual(labels = c("Terrestrial", "General", "Arboreal" ), 
                  values = c("1"="#d95f02", 
                                   "2"="#7570b3", 
                                   "3"="#1b9e77")) +
scale_fill_manual(labels = c("Terrestrial", "General", "Arboreal" ), 
                  values = c("1"="#d95f02", "2"="#7570b3", "3"="#1b9e77"),                      guide = F) + 
labs(x = "IM Index",
     center = F,
    color = "State") +
  #coord_cartesian(xlim=c(0.6, 1)) +
  theme_minimal() + 
  theme_ridges(center = T) +
    theme(axis.title.y = element_blank(), axis.title.x = element_text(size=7), axis.text.y  = element_text(size=4), axis.text.x = element_text(size=4), legend.position="none")

mei_plot

output_file = "20181101_i_eff_IM.pdf"

ggsave(output_file, width = 9, height = 6)
```

PES

```{r}
p_eff <- marginal_effects(pes.fits_comb, "PES", categorical = T, probs = c(0.1, 0.9))
```

Looks good!
```{r}
mep_plot <- plot(p_eff, plot = FALSE)[[1]] + 
scale_color_manual(labels = c("Terrestrial", "General", "Arboreal" ), 
                  values = c("1"="#d95f02", 
                                   "2"="#7570b3", 
                                   "3"="#1b9e77")) +
scale_fill_manual(labels = c("Terrestrial", "General", "Arboreal" ), 
                  values = c("1"="#d95f02", "2"="#7570b3", "3"="#1b9e77"),                      guide = F) + 
labs(x = "PES Index",
    center = F,
    color = "State") +
  theme_minimal() + 
  theme_ridges(center = T) +  
  theme(axis.title.y = element_blank(), axis.title.x = element_text(size=7), axis.text.y  = element_text(size=4), axis.text.x = element_text(size=4),legend.position="none") 
mep_plot

output_file = "20181101_p_eff_PES.pdf"

ggsave(output_file, width = 9, height = 6)
```

TAIL
```{r}
t_eff <- marginal_effects(tail.fits_comb, "TAIL", categorical = T, probs = c(0.1, 0.9))
```

Looking good
```{r}
met_plot <- plot(t_eff, plot = FALSE)[[1]] + 
scale_color_manual(labels = c("Terrestrial", "General", "Arboreal" ), 
                  values = c("1"="#d95f02", 
                                   "2"="#7570b3", 
                                   "3"="#1b9e77")) +
scale_fill_manual(labels = c("Terrestrial", "General", "Arboreal" ), 
                  values = c("1"="#d95f02", "2"="#7570b3", "3"="#1b9e77"),                      guide = F) + 
labs(x = "TAIL Index",
     center = F,
    color = "State") +
  theme_minimal() + 
  theme_ridges(center = T) +
      theme(axis.title.y = element_blank(), axis.title.x = element_text(size=7), axis.text.y  = element_text(size=4), axis.text.x = element_text(size=4), legend.position="none")

met_plot

output_file = "20181101_t_eff_TAIL.pdf"

ggsave(output_file, width = 9, height = 6)
```

PLOT ALL

```{r}
me_plot <- plot_grid(mem_plot,mei_plot,mep_plot,met_plot, ncol = 2, nrow = 2 )
save_plot("20181101_me_plot.pdf", me_plot, base_width = 8, base_height = 4)
```


